Inferring Galactic Parameters from Chemical Abundances with Simulation-Based Inference

### 2024-12-18 src/tex/ms.tex
[showyourwork] overleaf sync

Despite the additional complexity introduced by using multiple stellar data-points, our NN simply needs to predict the birth-time abundances for a single star (with index $i$) given a set of six parameters; $\{\vec\Lambda,\vec\Theta_i,T_i\}$. The same NN can be used for all $n_\mathrm{stars}$ stars (and run in parallel), reducing a set of $n_\mathrm{stars}$ runs of \texttt{Chempy} to a single matrix computation. With the above network parameter choices, the NN predicts abundances with an absolute percantage error of $1.6_{-0.9}^{+2.4}$\,\%, which is far below typical observational errors and even smaller away from the extremes of parameter space.
Our NN emulator is publicly available on the github repository accompanying this manuscript \href{https://github.com/TobiBu/sbi-chempy}{https://github.com/TobiBu/sbi-chempy}. \textcolor{red}{adapt to point to final folder on the repo. and maybe add zenodo link for the nueral network weights...}

>>>>

Despite the additional complexity introduced by using multiple stellar data-points, our NN simply needs to predict the birth-time abundances for a single star (with index $i$) given a set of six parameters; $\{\vec\Lambda,\vec\Theta_i,T_i\}$. The same NN can be used for all $n_\mathrm{stars}$ stars (and run in parallel), reducing a set of $n_\mathrm{stars}$ runs of \texttt{Chempy} to a single matrix computation. With the above network parameter choices, the NN predicts abundances with an absolute percantage error of \variable{output/ape_NN.txt}, which is far below typical observational errors and even smaller away from the extremes of parameter space.
Our NN emulator is publicly available on the github repository accompanying this manuscript \href{https://github.com/TobiBu/sbi-chempy}{https://github.com/TobiBu/sbi-chempy}. \textcolor{red}{adapt to point to final folder on the repo. and maybe add zenodo link for the nueral network weights...}
